A holomorphic approach to membranes and fivebranes

### 2022-07-06 fivebranes/kr.tex
merge

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

\section{Kac-Rudokov}

@@

\subsection{The fivebrane decomposition of $E(5|10)$}

@@

As above, we denote by $\{z_i\}$ the local coordinates along the fivebrane $Z=\C^3$ and $\{w_a\}$ the transverse holomorphic coordinates to the zero section in the fivefold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.

@@

\subsection{Irreducible representations of $E(3|6)$}
We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ we then see that it carries an induced consistent $\Z$-grading by degree. 
Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
One can check that the algebra is supported in degrees $j \geq -2$ so that as a super vector space
\[
E(3|6) = \prod_{j \geq -2} \fg_j
\]
where for small values of $j$ we have:
\begin{itemize}
\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is a completely even super vector space. 
\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is a completely odd super vector space.
\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is a completely even super vector space.
Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
\[
h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
\]
The Cartan of $\lie{sl}(2)$ is spanned by
\[
h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
\]
The Cartan of $\lie{gl}(1)$ is spanned by
\[
Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
\]
\end{itemize}

@@

The irreducible modules that we consider are constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
Denote by $\fg = E(3|6)$ and let 
\[
\fg_{<0} = \fg_{-2} \oplus \fg_{-1} , \quad \lie{g}_{>0} = \oplus_{j>0} \fg_j 
\]
so that $\fg = \fg_{<0} \oplus \fg_0 \oplus \fg_{>0}$. 
Given a $\fg_0$-module $V$ let 
\beqn\label{eqn:verma1}
M (V) \define U(\fg) \otimes_{U(\fg_{\geq 0})} V 
\eeqn
be the induced $\fg$-module. 
Notice that as super vector spaces~$M(V) = \Sym(\fg_{<0}) \otimes_\C V$.

@@

An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
\begin{align*}
\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
 y & = \lambda(Y)\in \C . 
\end{align*}
There is an isomorphism of $\fg_0$-modules
\begin{align*}
V_A^{p,r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
V_B^{p,-r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2) .
\end{align*} 
Note for type $A,B$ we have $\lambda_2 = 0$. 
To simplify notation we will write 
\begin{align*}
F_A(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
F_B(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2)  
\end{align*}
and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules \eqref{eqn:verma1}.

@@

@@

\begin{thm}[\cite{KR2}]
Consider the decomposition \eqref{eqn:decomp1} of the super Lie algebra
\beqn
E(5|10) = \til V_{-1} \times \prod_{i \geq -1} V_n
\eeqn
where $V_0 \simeq E(3|6)$. 
Then, as $E(3|6)$-modules there are isomorphisms 
\begin{align*}
\til V_{-1}^* & \simeq I_A(0,1) \\
E(3|6)^* = V_0^* & \simeq I_A(1,0) \\
V_j^* & \simeq I_B(0,j-1), \quad j \geq 1
\end{align*}
where $(-)^*$ denotes the topological dual.
\end{thm}

@@

The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory.
As a factorization algebra on the three-fold $Z$ the $!$-dual factorization algebra $\Obs_{sugra}|_Z$ is of the form $\clie_\bu (\Bar{\pi}_* \cL_{sugra,c})$ where $\Bar{\pi}_* \cL_{sugra}$ is an infinite-dimensional local Lie algebra on $Z$ which admits a (non-cohomological) weight grading
\beqn\label{eqn:decomp2a}
\Bar{\pi}_* \cL_{sugra} = \bigoplus_{n \geq -1} \Omega^{0,\bu}(Z, \cV^{(n)}) 
\eeqn
where $\cV^{(n)}$ is some holomorphic vector bundle on $Z$.

For the remainder of this section we focus on the case $Z = \C^3$. 
Our goal is to relate this decomposition to the purely algebraic one of \cite{KR1} that we just recalled.
In turn, this will give us a description of fivebrane local operators supported at $0 \in \C^3$ in terms of irreducible representations of the super Lie algebra $E(3|6)$.

First, we recall the precise relationship between the central extension of the super Lie algebra $E(5|10)$ and the local Lie algebra~$\cL_{sugra}$ on~$\R \times \C^5$.
The local $L_\infty$ algebra $\cL_{sugra}$ on $\R \times \C^5$ can be written as 
\[
\cL_{sugra} = \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5, L) \simeq \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5) \otimes L_0 ,
\]
where $L$ is a translation invariant holomorphic vector bundle and~$L_0$ its fiber over~$0 \in \C^5$.
As in \S \ref{s:interacting}, the local $L_\infty$ algebra structure on $\cL_{sugra}$ induces an $L_\infty$ structure on the $\infty$-jets at~$0 \in \R \times \C^5$ of $\cL_{sugra}$, which we can identify using the Poincar\'e lemma with~$L_0[[z_1,\ldots,z_5]]$.
Furthermore, the Taylor expansion map at $0 \in \R \times \C^5$ defines an $L_\infty$ map
\[
\cL_{sugra}(\R \times \C^5) \to L_0[[z_1,\ldots,z_5]] .
\]

In~\cite{RSW} it is shown that $L_0[[z_1,\ldots,z_5]]$ is equivalent to the super Lie algebra $\Hat{E(5|10)}$ which is the central extension of $E(5|10)$ by the cocycle in \brian{finish}. 
There is a similar result for the restricted local $L_\infty$ algebra $\Bar{\pi}_*\cL_{sugra}$.

If we take the threefold $Z = \C^3$ then of course $\R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2) \simeq \R \times \C^5$.

%First, we will see how to relate the decomposition at the level of global sections of~$\cL_{sugra}$ over~$Z = \C^3$.

\subsection{Character computations}

Define the (super) character of an $E(3|6)$-module $M$ by the formula
\[
\ch \, M  \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
\]
As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
\[
M(V) = \Sym(\lie{g}_{<0}) \otimes V .
\]

Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.

Given this description, there is a simple expression for the character 
\[
\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-\frac32 y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
\]
where $R = \ch \Sym(\fg_{<0})$.

@@

For notational simplicity, we will set $q = t^2$.

There is a cohomological description of the irreducible modules of type $A$
\[
I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
\eeqn
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

\parsec[s:typeAunrefinedKR]
In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
From the long exact sequence \eqref{eqn:les1} we have the following expression 
\[
\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} = \sum_{j \geq 0} \ch M(\lambda_1+j,0,\lambda_3+j;\frac23 \lambda_1 - \lambda_3 - \frac{j}{3}) .
\]

Let $M_j$ be the $j$th Verma module appearing in the sum above. 
Then
\beqn
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \left(r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \right) .
\eeqn
Notice that 
\[
r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
\]
so the above expression for $\ch M_j$ reduces to
\[
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} t^j .
\]
Observe the formal identity 
\[
\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
\]
where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.

Using this identity, we evaluate
\begin{align*}
\ch I_A(\lambda_1,\lambda_3) & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\ 
& = \frac{t^{3 \lambda_3-2\lambda_1}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p(tr) (1-tr^{-1})^3 - r^{-\lambda_3-2} p(tr^{-1})(1-tr)^3 \right) .
\end{align*}

>>>>

\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
\usepackage{macros-fivebrane}
%
\begin{document}

\section{A series of finite $N$ conjectures}

@@

\subsection{The fivebrane decomposition of $\Hat{E(5|10)}$}

@@

As above, we denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.

@@

The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory.
The $!$-dual of the factorization algebra $\Obs_{sugra}|_Z$ is of the form $\clie_\bu (\cG_c)$ where $\cG$ is an infinite-dimensional local $L_\infty$ algebra on $Z$.
In \S \ref{s:weight1} we defined a $\C^\times$ action on $\cG$ which determines a (non-cohomological) weight grading
\beqn\label{eqn:decomp2a}
\cG = \bigoplus_{n \geq -1} \Omega^{0,\bu}(Z, \cV^{(n)}) 
\eeqn
where $\cV^{(n)}$ is some holomorphic vector bundle on $Z$.

For the remainder of this section we focus on the case $Z = \C^3$. 
Our goal is to show that this weight grading is compatible with the one on the central extension of $E(5|10)$ that we recalled in \S \ref{s:e510central}. 
In turn, this will give us a description of fivebrane local operators supported at $0 \in \C^3$ in terms of irreducible representations of the super Lie algebra $E(3|6)$.

First, we recall the precise relationship between the central extension of the super Lie algebra $E(5|10)$ and the local Lie algebra~$\cL_{sugra}$ on~$\R \times \C^5$.
The local $L_\infty$ algebra $\cL_{sugra}$ on $\R \times \C^5$ can be written as 
\[
\cL_{sugra} = \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5, L) \simeq \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5) \otimes L_0 ,
\]
where $L$ is a translation invariant holomorphic vector bundle and~$L_0$ its fiber over~$0 \in \C^5$.
As in \S \ref{s:interacting}, the local $L_\infty$ algebra structure on $\cL_{sugra}$ induces an $L_\infty$ structure on the $\infty$-jets at~$0 \in \R \times \C^5$ of $\cL_{sugra}$, which we can identify using the Poincar\'e lemma with~$L_0[[z_1,\ldots,z_5]]$.
Furthermore, the Taylor expansion map at $0 \in \R \times \C^5$ defines an $L_\infty$ map
\beqn
T_0 \colon \cL_{sugra}(\R \times \C^5) \to L_0[[w_1,w_2, z_1,z_2,z_3]] 
\eeqn
where we recall that we have used $\{z_i\}$ for the coordinates along the directions the fivebrane wraps in 
\[
\C^5 \simeq {\rm Tot}(K^{1/2}_Z \otimes \C^2)
\]
and $\{w_a\}$ for the transverse holomorphic coordinates.

In~\cite{RSW} it is shown that $L_0[[w_1,w_2, z_1,z_2,z_3]]$ is equivalent to the super Lie algebra $\Hat{E(5|10)}$ which is the central extension of $E(5|10)$ by the cocycle in \brian{finish}. 
The restricted local $L_\infty$ algebra $\cG$ sits somewhere in-between $\cL_{sugra}(\R \times \C^5)$ and $\Hat{E(5,10)}$.

The sheaf of local $L_\infty$ algebras $\cG$ on $\C^3$ is the smooth sections of a holomorphic translation invariant pro vector bundle $G$. 
Let $G_0$ be the fiber over $0 \in \C^3$. 
Similarly as above, since the space $G_0[[z_1,z_2,z_3]]$ is the $\infty$-jets of $\cG$ at $0 \in \C^3$ it is equipped with the structure of an $L_\infty$ algebra and the Taylor expansion map 
\[
T_0^{\C^3} \colon \cG(\C^3) \to G_0[[z_1,z_2,z_3]] 
\]
is a map of $L_\infty$ algebras.

\begin{lem}
\begin{itemize}
\item[(1)]
There is an equivalence of $L_\infty$ algebras
\[
\Hat{E(5|10)} \simeq G_0 [[z_1,z_2,z_3]] .
\]
\item[(2)]The partial Taylor expansion of sections of $\cL_{sugra}(\R \times \C^5)$ at $w_1=w_2 = 0$ defines a map of $L_\infty$ algebras 
\[
\cL_{sugra}(\R \times \C^5) \to \cG(\C^3) ,
\]
and makes the following diagram commute
\[
\begin{tikzcd}
\cL_{sugra}(\R \times \C^5) \ar[dr,dotted] \ar[rr,"T_0^{\R \times \C^5}"] & &  \Hat{E(5|10)} \\ 
& \cG(\C^3) \ar[ur,"T_0^{\C^3}"'] & .
\end{tikzcd} 
\]
\item[(3)] 
The Taylor expansion map $T_0^{\C^3}$ is $\C^\times$-equivariant. 
\end{itemize}
\end{lem}
%First, we will see how to relate the decomposition at the level of global sections of~$\cL_{sugra}$ over~$Z = \C^3$.

In \S \ref{s:}. \brian{finish}

\subsection{Irreducible representations of $E(3|6)$}
We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of the central extension of $E(5|10)$ we see that it carries an induced consistent $\Z$-grading by degree. 
Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
One can check that the algebra is supported in degrees $j \geq -2$ so that as a super vector space
\[
E(3|6) = \prod_{j \geq -2} \fg_j
\]
where for small values of $j$ we have:
\begin{itemize}
\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is a completely even super vector space. 
\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is a completely odd super vector space.
\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is a completely even super vector space.
Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
\[
h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
\]
The Cartan of $\lie{sl}(2)$ is spanned by
\[
h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
\]
The Cartan of $\lie{gl}(1)$ is spanned by
\[
Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
\]
\end{itemize}

@@

We are interested in a class of irreducible modules for $E(3|6)$ that can be constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
Denote by $\fg = E(3|6)$ and let 
\[
\fg_{<0} = \fg_{-2} \oplus \fg_{-1} , \quad \lie{g}_{>0} = \oplus_{j>0} \fg_j 
\]
so that $\fg = \fg_{<0} \oplus \fg_0 \oplus \fg_{>0}$. 
Given a $\fg_0$-module $V$ let 
\beqn\label{eqn:verma1}
M (V) \define U(\fg) \otimes_{U(\fg_{\geq 0})} V 
\eeqn
be the induced $\fg$-module. 
Notice that as super vector spaces~$M(V) = \Sym(\fg_{<0}) \otimes_\C V$.

@@

An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2,\lambda_3,y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
\begin{align*}
\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
 y & = \lambda(Y)\in \C . 
\end{align*}
Actually, for the remainder of this section we will be interested in the case $\lambda_2 = 0$; the modules with $\lambda_2 \ne 0$ will play no role.

For $\lambda_1,\lambda_3 \geq 0$ there are isomorphisms of $\fg_0$-modules
\begin{align*}
V_A^{\lambda_1,\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 - \lambda_3) \\
V_B^{\lambda_1,-\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 + \lambda_3 +2) .
\end{align*} 
To simplify notation we will get rid of the dependence on $\lambda_2$ and write 
\begin{align*}
F_A(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
F_B(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2)  
\end{align*}
and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules \eqref{eqn:verma1}.

@@

In \textit{loc. cit.} they refer to such irreducible modules $I_A,I_B$ as `degenerate'.

@@

\begin{thm}[\cite{KR2}]
Consider the decomposition \eqref{eqn:decomp1} of the super Lie algebra
\beqn
E(5|10) = \til V_{-1} \times \prod_{i \geq -1} V_n
\eeqn
where $V_0 \simeq E(3|6)$. 
Then, there are isomorphisms of $E(3|6)$-modules
\begin{align*}
\til V_{-1}^* & \simeq I_A(0,1) \\
E(3|6)^* = V_0^* & \simeq I_A(1,0) \\
V_j^* & \simeq I_B(0,j-1), \quad j \geq 1
\end{align*}
where $(-)^*$ denotes the topological dual.
\end{thm}

@@

The (super) character of an $E(3|6)$-module $M$ is given by the formula
\[
\ch \, M  \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
\]
Our goal in this section is to compute the explicit formula for the character of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$.

As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
\[
M(V) = \Sym(\lie{g}_{<0}) \otimes V .
\]

%Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.

For type $A$ degenerate modules we start with the $\fg_0$-module 
\[
V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
\] 
given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
There is thus a simple expression for the character 
\beqn\label{eqn:MA}
\ch\, {M_A(\lambda_1,\lambda_3)} = q^{-\frac32 y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) 
\eeqn
where $R = \ch \Sym(\fg_{<0})$ and 
\[
\ch(V_A^{\lambda_1,\lambda_3}) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
\]
is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
In this expression $\ch_{SU(3)}^{\lambda_1}$ is the character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1,0)$ and $\ch^{\lambda_3}_{SU(2)}$ is the character of the irreducible $SU(2)$ representation of highest weight $\lambda_3$.

@@

Before moving on, we point out that in the formula for $R$ if we specialize $t_1=t_2=1$we obtain
\[
R(q,r) = \frac{(1-q^{1/2}r)^3 (1-q^{1/2} r^{-1})^3}{(1-q)^3} .
\]
Finally, in the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.

To obtain the formula for the character we will use a cohomological description of the irreducible modules of type $A$
\[
I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
\eeqn
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

\parsec[s:typeAunrefinedKR]
In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
From the long exact sequence \eqref{eqn:les1} we have the following expression 
\beqn
\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
\eeqn 
We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term
\beqn
\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
\eeqn

Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
\begin{align*}
\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{-\lambda_1-j} t_2^{\lambda_1 + j} \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
%\\ 
%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
\end{align*}
and $SU(2)$ character
\begin{align*}
\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
\end{align*}

Given these formulas we see that we need to compute the sum
\begin{multline}
\sum_{j \geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{1}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
= \sum_{k=0}^{\lambda_1+j} \sum_{l=0}^k 
\end{multline}

Combining with the formula for $R(t,r,t_1,t_2)$ we arrive at the formula
\begin{multline} 
\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} 
\end{multline}

\parsec

\beqn
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \left(r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \right) .
\eeqn
Notice that 
\[
r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
\]
so the above expression for $\ch M_j$ reduces to
\[
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} t^j .
\]
Observe the formal identity 
\[
\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
\]
where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.

Using this identity, we evaluate
\begin{align*}
\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\ 
& = \frac{t^{3 \lambda_3-2\lambda_1}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p(tr) (1-tr^{-1})^3 - r^{-\lambda_3-2} p(tr^{-1})(1-tr)^3 \right) .
\end{align*}

In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character specializes to
\[
\ch I_A(1,0)|_{t_1=t_2=1} = \frac{r^2}{(1-t^2)^3} \left[ t^2 (r^2 + r^{-2} + 1) - 3 t (r + r^{-1}) + 3 \right] .
\]
